Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-23 R0V0.tex
Finish reviwing the examples

\mypara To that end three methodologies are recalled below: chordal graphs, alternating direction of multipliers (ADMM) and scaled diagonal dominance. The first exploits the network topology to decompose it into smaller connected components. The second method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality below. Finally, scaled diagonal dominance exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling. Note that these methodologies can be used either separately or together. The latter would appropriate, when the smaller components of the network have high rank. Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.

\mypara Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.

@@

\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}. Consider the case with $N=4$.

@@

\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

\mypara To show the advantages of the method proposed in this paper, a benchmark was run for a network composes by $N=4$ systems and in three scenarios, according to the constraints imposed on the matrix $Y$. Namely, the unconstrained case, the ``neighbor case'', and the fully decentralized (diagonal) case. For the two latter cases, it was possible to consider up to $N=256$ systems for the ``neighbor case'' and up to $N=512$ systems for the fully decentralized (diagonal) case.

@@

\mypara In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$. The sets $\mathbf{C}$ are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}(1)&=&\{\begin{bmatrix}
		1,&1,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(2)&=&\{\begin{bmatrix}
		1,&1,&1,&1,&1,&1,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(3)&=&\{\begin{bmatrix}
		0,&0,&1,&1,&1,&1,&1,&1\end{bmatrix}\},\\
		\mathbf{C}(4)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&1,&1,&1,&1\end{bmatrix}\}\;.
	\end{array} 
\end{equation*}

@@

\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0&0&0\\
 	0&\overline{Y}_2(\cdot)&0&0\\
 	0&0&\overline{Y}_3(\cdot)&0\\
 	0&0&0&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}\;.
\end{equation*}

\mypara In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\{q_i\}$. Moreover, the sets $\mathbf{C}$ are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}(1)&=&\{\begin{bmatrix}
		1,&1,&0,&0,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(2)&=&\{\begin{bmatrix}
		0,&0,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(3)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&1,&1,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(4)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&0,&0,&1,&1\end{bmatrix}\}\;.
	\end{array} 
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the matrix $W$ 
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix}
\end{align*}

\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this illustration: unconstrained, ``neighbor'' and fully decentralized.

@@

\mypara According to the graph shown in Figure \ref{fig:time graph}, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} was of the same order of magnitude for the three cases. However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor''-constrained case which, in turn, takes more time than the fully decentralized-constrained case. The time difference between the two latter cases can be explained by fact that, for the ``neighbor'' case, the matrix $Y$ contains more non-identically zero elements than the fully decentralized case. In addition to this, in the former case, each element is defined as a polynomial of second degree on the variables $q_i$ and $\breve{q}_i$, while for the latter, they are defined on the variable $q_i$ only.

\mypara Regarding the on-line integration phase, since the matrices $W$ computed in each case is  constant, for each index $i\in\mathbb{N}_{[1,4]}$, the geodesic curve connecting the origin to a point $q_i\in\mathbb{R}^2$ is a straight line: $\gamma_i(s)=sq_i$, where $s\in[0,1]$. For each case, and for each index $i\in\mathbb{N}_{[1,4]}$, the feedback law is  given by the formula
\begin{equation*}
	k= \int_0^1Y(sq)W^{-1}q\,ds.
\end{equation*}
Given the structure of the matrices $Y$ and $W$, each line $i\in\mathbb{N}_{[1,4]}$ is given by
\begin{equation*}
k_i=\begin{cases}
	\displaystyle\int_0^1Y_i(sq)W_i^{-1}q_i\,ds,&\text{if unconstrained}\\
	\displaystyle\int_0^1Y_i(sq_i,s\breve{q}_i)W_i^{-1}q_i\,ds,&\text{if ``neighbor''}\\
	\displaystyle\int_0^1Y_i(sq_i)W_i^{-1}q_i\,ds,&\text{if fully decentralized.}
\end{cases}
\end{equation*}
Moreover, from Theorem~\ref{thm:main result}, the feedback law $k$ solves Problem~\ref{problem formulation} for the network resulting from the interconnection of systems \eqref{eq:example}.

@@

@@

\mypara Consider the with four agents (i.e., $N=4$) network having the topology illustrated in Figure~\ref{fig:cycle graph}.

@@

>>>>

\mypara To that end three methodologies are recalled below: chordal graphs, alternating direction of multipliers (ADMM) and scaled diagonal dominance. The first exploits the network topology to decompose it into smaller complete components. The second method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below). Finally, scaled diagonal dominance exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling. Note that these methodologies can be used either separately or together. The latter would appropriate, when the smaller components of the network have high rank and the computing platform where the solver runs has memory limitations.

\mypara Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.  onsider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.

@@

\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}. Consider the case with $N=4$. Two different methods are employed to compute the matrix $W$, namely, chordal graphs and ADMM.

@@

\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials and the MI \eqref{eq:MI formulation} could not be solved. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

\mypara To show the advantages of the method proposed in this paper, a benchmark composed of  three scenarios, according to the constraints imposed on the matrix $Y$, has been created.  Namely, the unconstrained case, the ``neighbor'' case, and the fully decentralized case. For the two latter cases, it was possible to consider up to $N=256$ systems for the ``neighbor'' case and up to $N=512$ systems for the fully decentralized (diagonal) case. In these scenarios the techniques provided by chordal graphs have been employed.

@@

\mypara In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. To comply with this requirement, the set $\mathscr{K}$ is defined as $\mathscr{K}(1)=\{1,2\}$, $\mathscr{K}(4)=\{3,4\}$ and $\mathscr{K}(i)=\{i-1,i,i+1\}$, for each index $i=2,3$. The sets $\mathbf{C}$ are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}(1)&=&\{\begin{bmatrix}
		1,&1,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(2)&=&\{\begin{bmatrix}
		1,&1,&1,&1,&1,&1,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(3)&=&\{\begin{bmatrix}
		0,&0,&1,&1,&1,&1,&1,&1\end{bmatrix}\},\\
		\mathbf{C}(4)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&1,&1,&1,&1\end{bmatrix}\}\;.
	\end{array} 
\end{equation*}

@@

\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0&0&0\\
 	0&\overline{Y}_2(\cdot)&0&0\\
 	0&0&\overline{Y}_3(\cdot)&0\\
 	0&0&0&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}, i\in\mathbb{N}_{[1,4]}\;.
\end{equation*}

\mypara In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\{q_i\}$. Moreover, the sets $\mathbf{C}$ are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}(1)&=&\{\begin{bmatrix}
		1,&1,&0,&0,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(2)&=&\{\begin{bmatrix}
		0,&0,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(3)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&1,&1,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(4)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&0,&0,&1,&1\end{bmatrix}\}\;.
	\end{array} 
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the matrix $W$ 
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}

\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this topology: unconstrained, ``neighbor'' and fully decentralized.  According to this graph shown, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} has the same order of magnitude for the three cases. However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor'' case which, in turn, takes more time than the fully decentralize case. The time difference between the two latter cases can be explained by fact that, for the ``neighbor'' case, the matrix $Y$ contains more non-identically zero elements than the fully decentralized case. In addition to this, in the former case, each element is defined as a polynomial of second degree on the variables $q_i$ and $\breve{q}_i$, while for the latter, they are defined on the variable $q_i$ only.

@@

@@

\mypara Regarding the on-line integration phase, since the matrices $W$ computed in each case are  constant, for each index $i\in\mathbb{N}_{[1,4]}$, the geodesic curve connecting the origin to a point $q_i\in\mathbb{R}^2$ is a straight line: $\gamma_i(s)=sq_i$, where $s\in[0,1]$. For each index $i\in\mathbb{N}_{[1,4]}$ and assuming that $u^\ast\equiv0$, the feedback law is  given by the formula
\begin{equation*}
	k= \int_0^1Y(sq)W^{-1}q\,ds.
\end{equation*}
Given the structure of the matrices $Y$ and $W$, each line $i\in\mathbb{N}_{[1,4]}$ is given by
\begin{equation*}
k_i=\begin{cases}
	\displaystyle\int_0^1Y_i(sq)W_i^{-1}q_i\,ds,&\text{if unconstrained}\\
	\displaystyle\int_0^1Y_i(sq_i,s\breve{q}_i)W_i^{-1}q_i\,ds,&\text{if ``neighbor''}\\
	\displaystyle\int_0^1Y_i(sq_i)W_i^{-1}q_i\,ds,&\text{if fully decentralized.}
\end{cases}
\end{equation*}
Moreover, from Theorem~\ref{thm:main result}, the feedback law $k$ solves Problem~\ref{problem formulation} for the network resulting from the interconnection of systems \eqref{eq:example}.

@@

\mypara Consider the with network with four agents (i.e., $N=4$) with the topology illustrated in Figure~\ref{fig:cycle graph}. Also in this topology, chordal graphs and ADMM are employed to solve the MIs~\eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual}, respectively.

@@

\mypara The online computation of the feedback law for the network composed of subsystems of the form \eqref{eq:example} is analogous to what has been shown to the chain-topology case.
